Verifying Demonstrations

### 2018-02-27 paper/analysis.tex
Adding performance section
Adding two new subsections

\subsection{Assumptions}

@@

@@

>>>>

\subsection{Assumptions} \label{assumptions}

@@

\section{Performance and implementation}

\subsection{Implementation on smartphones}
Technological progress has enabled more advanced cryptography on Smart-cards and Smartphones which could be used to implement our solution : Benchmarks have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in  \SI{153}{\milli\second}. However, those benchmarks also demonstrate that SmartCards remain slow to process complex protocols such as Idemix  (taking between \SI{4}{\second} and \SI{8}{\second} to process it), despite promising efforts such as the IRMA project.

@@

\subsection{Blockchain feasability}
